---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dts

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.org/poissonconsulting/dts.svg?branch=master)](https://travis-ci.org/poissonconsulting/dts)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/dts?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/dts)
[![Coverage status](https://codecov.io/gh/poissonconsulting/dts/branch/master/graph/badge.svg)](https://codecov.io/github/poissonconsulting/dts?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)

`dts` is a light-weight R package to manipulate data frames with a Date or POSIXct column and one or more double columns representing time series values.
    
## Installation

To install the latest development version from [GitHub](https://github.com/poissonconsulting/dts)
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/dts")
```

To install the latest development version from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("dts")
```

## Citation

```{r, comment="", echo=FALSE}
citation(package = "dts")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/dts/issues).

[Pull requests](https://github.com/poissonconsulting/dts/pulls) are always welcome.

Please note that the 'dts' project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
